### 2024-06-05 preregistration/README.qmd
add pdf download link to prereg

---
title: ""
format: 
  html:
    css: D:/repositories/liss_ef_2024/assets/style.css
    template: ../assets/template.html
    keep_md: true
bibliography: ../manuscript/references.bib
csl: ../manuscript/apa.csl
link-citations: true
editor: 
  markdown: 
    wrap: sentence
---

>>>>

---
title: ""
format: 
  html:
    css: ../assets/style.css
    template: ../assets/template.html
bibliography: ../manuscript/references.bib
csl: ../manuscript/apa.csl
link-citations: true
editor: 
  markdown: 
    wrap: sentence
---
